Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Update Moltres.tex

Although the qualitative agreement is decent, there are discrepancies between
the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
the hottest channel. The peak graphite temperature is around 14 K larger in the
Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
roughly 20\%. These are not insignificant differences. However, given the
differing nature of the two models--no axial conduction in the \gls{MSRE} model,
2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
Moltres calculation--we believe this variation in quantitative behavior is
acceptable for the purpose of this work, which is to introduce Moltres as a
simulation tool. One additional feature that could influence Moltres results is
inclusion of precursor decay heat; this is under active development. Trustworthy
verification of Moltres results, such as spatial flux and temperature profiles,
will require more detailed experimental measurements than those available in the
\gls{ORNL} technical reports, which contain only macroscopic data such as
steady-state power and heat-exchanger temperature drops. Additionally, detailed
comparison with other modern modeling efforts such as that conducted in
\cite{aufiero_development_2014,laureau_transient_2017} is desirable. In that
vein, a collaboration is under way with the primary author of
\cite{aufiero_develoment_2014} to try and reproduce calculation results from
OpenFOAM. We hope to publish the results of this comparison in a future work.

>>>>

Although the qualitative agreement is decent, there are discrepancies between
the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
the hottest channel. The peak graphite temperature is around 14 K larger in the
Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
roughly 20\%. These are not insignificant differences. However, given the
differing nature of the two models--no axial conduction in the \gls{MSRE} model,
2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
Moltres calculation--we believe this variation in quantitative behavior is
acceptable for the purpose of this work, which is to introduce Moltres as a
simulation tool. One additional feature that could influence Moltres results is
inclusion of precursor decay heat; this is under active development. Trustworthy
verification of Moltres results, such as spatial flux and temperature profiles,
will require more detailed experimental measurements than those available in the
\gls{ORNL} technical reports, which contain only macroscopic data such as
steady-state power and heat-exchanger temperature drops. Additionally, detailed
comparison with other modern modeling efforts such as that conducted in
\cite{aufiero_development_2014,laureau_transient_2017} is desirable. In that
vein, a collaboration is under way with the primary author of
\cite{aufiero_develoment_2014} to try and reproduce calculation results from
OpenFOAM. Further, Dr. Collins from \cite{turner_virtual_2016} has expressed interest
in comparing Moltres results against MSR-VERA in order to quantify errors resulting
from usage of multigroup diffusion in comparison to 2D-1D method of characteristics fine group solutions.
We hope to publish the results of these comparisons in a future work.
